Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/inverted_u.tex
fix table lines
more table edits'
fixups to table

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table*}[h]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c}{Heavy-Tail} 
  & \multicolumn{3}{c}{Needle-in-Haystack}\\
  \hline 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG 
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)} 
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)} 
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)} 
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$ 
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)} 
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)} 
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)} 
  \\
\hline
  $\DG$ vs $\DEG$ 
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)} 
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)} 
  \\
   \hline
\end{tabular}
\caption{The duopoly experiment for Uniform and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. The first line in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. 
The second line specifies the ``effective end of game" (\Eeog): the average and the median (in brackets).
\ascomment{Can't add vertical lines in the top row - pls help!}}
\label{sim_ht}
\end{table*}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$ 
    & \makecell{\textbf{0.003}$\pm$0.003} 
    & \makecell{\textbf{0.083}$\pm$0.02} 
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$ 
    & \makecell{\textbf{0.045}$\pm$0.01} 
    & \makecell{\textbf{0.25}$\pm$0.02} 
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$ 
    & \makecell{\textbf{0.12}$\pm$0.02} 
    & \makecell{\textbf{0.36}$\pm$0.03} 
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\label{ht_incum}
\caption{The temporary monopoly experiment with $X=200$ (and $T_0=\asedit{???}$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the row) and the incumbent's algorithm (the column). The cell specifies the entrant's market share for the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\end{table}

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table*}[h]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Heavy-Tail} 
  & \multicolumn{3}{c|}{Needle-in-Haystack}\\
  \hline 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG 
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)} 
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)} 
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)} 
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$ 
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)} 
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)} 
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)} 
  \\
\hline
  $\DG$ vs $\DEG$ 
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)} 
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)} 
  \\
   \hline
\end{tabular}
\caption{The duopoly experiment for Uniform and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. The first line in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. 
The second line specifies the ``effective end of game" (\Eeog): the average and the median (in brackets).}
\label{sim_ht}
\end{table*}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$ 
    & \makecell{\textbf{0.003}$\pm$0.003} 
    & \makecell{\textbf{0.083}$\pm$0.02} 
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$ 
    & \makecell{\textbf{0.045}$\pm$0.01} 
    & \makecell{\textbf{0.25}$\pm$0.02} 
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$ 
    & \makecell{\textbf{0.12}$\pm$0.02} 
    & \makecell{\textbf{0.36}$\pm$0.03} 
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\label{ht_incum}
\caption{The temporary monopoly experiment with $X=200$ (and $T_0=20$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the row) and the incumbent's algorithm (the column). The cell specifies the entrant's market share for the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\end{table}
